Precise predictions for same-sign W-boson scattering at the LHC

### 2018-03-13 Draft/article.tex
Add MCnet preprint number
Add specific process IDs in VBFNLO description
Rewrite BONSAY section a bit

  Nikhef/2018-012, UWTHPH-2018-12, VBSCan-PUB-01-18,

  ZU-TH-08/18}
\end{abstract}
\thispagestyle{empty}
\vfill
\newpage
\setcounter{page}{1}

@@

    \item The program {\sc Bonsay} consists of a general-purpose Monte Carlo integrator written by Christopher Schwan and matrix elements taken from different sources:
    Born matrix elements are adapted from the program {\sc Lusifer}~\cite{Dittmaier:2002ap}, real matrix elements are written by Marina Billoni, and virtual matrix elements by Stefan Dittmaier.
    One loop integrals are evaluated using the {\sc Collier} library~\cite{Denner:2014gla,Denner:2016kdg}.
    For the fiducial cross sections it uses the VBS approximation at LO and NLO.
    The virtual corrections are additionally approximated using a double-pole approximation.
    For more inclusive cross sections at LO the exact matrix elements ($s$-channels, interferences) can also be used.

@@

      \item {\sc VBFNLO}~\cite{Arnold:2008rz, Arnold:2011wj, Baglio:2014uba} is a flexible
        parton-level Monte Carlo for processes with EW bosons. It
        allows the calculation of VBS processes at NLO QCD in the VBS
        approximation, with process IDs between 200 and 290. The corresponding
        $s$-channel contributions are available separately as tri-boson processes with
        semi-leptonic decays, with process IDs between 401 and 492. These can simply
        be added on top of the VBS contribution. Interferences between the two are therefore neglected.
        The usage of leptonic tensors in the calculation, pioneered in
        Ref.~\cite{Jager:2006zc}, thereby leads to a significant speed improvement over
        automatically generated code.  Besides the SM, also a variety of
        new-physics models including anomalous couplings of the Higgs and gauge
        bosons can be simulated.

>>>>

  MCnet-18-06, Nikhef/2018-012, UWTHPH-2018-12,

  VBSCan-PUB-01-18, ZU-TH-08/18}
\end{abstract}
\thispagestyle{empty}
\vfill
\newpage
\setcounter{page}{1}

@@

    \item The program {\sc Bonsay}~\cite{Dittmaier:2018zzz} consists of a general-purpose Monte Carlo integrator and matrix elements taken from different sources:
    Born matrix elements are adapted from the program {\sc Lusifer}~\cite{Dittmaier:2002ap}, which have been generalized to calculate also real matrix elements.
    Virtual matrix elements have been calculated using an in-house matrix element generator.
    One loop integrals are evaluated using the {\sc Collier} library~\cite{Denner:2014gla,Denner:2016kdg}.
    For the fiducial cross sections it uses the VBS approximation at LO and NLO.
    The virtual corrections are additionally approximated using a double-pole approximation.
    For more inclusive cross sections at LO the exact matrix elements ($s$-channels, interferences) can also be used.

@@

      \item {\sc VBFNLO}~\cite{Arnold:2008rz, Arnold:2011wj, Baglio:2014uba} is a flexible
        parton-level Monte Carlo for processes with EW bosons. It
        allows the calculation of VBS processes at NLO QCD in the VBS
        approximation, with process IDs between 200 and 290. Same-sign
        $\PW^+\PW^+jj$ production is provided via the process ID 250. The corresponding
        $s$-channel contributions are available separately as tri-boson processes with
        semi-leptonic decays, with process IDs between 401 and 492. For the
        final state studied in this article, only $\PW^+\PW^+\PW^-$
        production with a hadronically decaying $\PW^-$ boson, process ID 432,
        can contribute. These can simply be added on top of the VBS
        contribution. Interferences between the two are therefore neglected.
        The usage of leptonic tensors in the calculation, pioneered in
        Ref.~\cite{Jager:2006zc}, thereby leads to a significant speed improvement over
        automatically generated code.  Besides the SM, also a variety of
        new-physics models including anomalous couplings of the Higgs and gauge
        bosons can be simulated.
